Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
forged results. Go home and add pictures

\begin{table*}
\centering
\begin{tabular}{p{4cm}|p{4cm}|p{4cm}|p{4cm}}  %error metric is not interesting
\hline 
Example & Reducer Nodes & simulator & optimization\\
\hline 
Texture& Stratum, Column, LayeredMaterial & reflectance & Error diffusion \\
\hline
Subsurface scattering& Stratum, Column, LayeredMaterial & reflectance , transmittance & Branch and bound\\
\hline 
Caustics 1 & Column, QuadLayerMaterial & & SA \\
\hline 
Caustics 2 & Column, SubdivSurfMaterial & caustics & SPSA \\
\hline
Deformation & Column, LayeredMaterial& elasticity & Branch and bound\\
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:example}
\end{table*}

\subsection{Textured Model}
We expand the set of printable colors by stacking translucent materials. We then applied
dithering with our expanded colors.
Results are shown in Figure~\ref{fig:texture}

%\subsection{Print Material Characterization and Measurement}
%We used existing measurements of Objet print materials.
\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. 
In this example, we
tried to make the material as light as possible.

We tried different combinations of generators in this experiment.
We compared the performance of these different generator
in terms of run-time and error.
\begin{enumerate}
\item Spline for top layer, fine-grained voxelization for mid layer
and a coarse grid for bottom layer.
\item Voxels for top layer, splines for middle layer and a coarse
bottom layer.
\item Find-grained voxels for top layer and coarse grid for bottom layer.
\end{enumerate}

@@

\subsection{Caustics for a Mesh}
We demonstrate how to produce a 3D model with specific caustic shape under a particular lighting,
similar to \cite{Finckh:2010}. The difference is that we optimize on an arbitrary 3D model,
and we use a generic rendering package (NVidia optiX). 
We represented the surface with a spline surface.
Our algorithm took 6 hours to finish
with $4000$ spline control points for the model and $600\times 600$ resolution for the caustic image. A 
picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.

\begin{figure}
	\centering
 	\includegraphics[width=0.3\textwidth]{figure/caustic.jpg}
\caption{Teapot with a caustic image.}
\label{fig:caustic}
\end{figure}

>>>>

\begin{table*}
\centering
\begin{tabular}{p{4cm}|p{4cm}|p{4cm}|p{4cm}}  %error metric is not interesting
\hline 
Example & Reducer Nodes & simulator & optimization\\
\hline 
Texture& Stratum, Column, LayeredMaterial & reflectance & Error diffusion \\
\hline
Subsurface scattering& Stratum, Column, LayeredMaterial & reflectance , transmittance & Branch and bound\\
\hline 
Caustics 1 & Column, QuadLayerMaterial & & SA \\
\hline 
Caustics 2 & Column, SubdivSurfMaterial & caustics & SPSA \\
\hline
Deformation & Column, LayeredMaterial& elasticity & Branch and bound\\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:example}
\end{table*}

\subsection{Textured Model}
We expand the set of printable colors by stacking translucent materials.
We then applied dithering with our expanded colors.
Results are shown in Figure~\ref{fig:texture}
\subsection{Subsurface Scattering}
We replicated \cite{Hasan:2010} using our framework.

\subsection{Refractive Caustics}
We replicated two algorithms 
presented in \cite{Marios:2011} and \cite{Finckh:2010} for computing goal-based caustics.
The first version computes a 2D grid of micro-lenses. 
The optimization permutes the location of the micro-lenses using SA to achieve a smooth surface.
This algorithm doesn't require any simulation.

In the second algorithm , we used subdivision surfaces to represent the surface for simplicity.
The original algorithm used B-spline surfaces.
We used a generic caustics shader for height field 
instead of a specialized shader for spline surfaces.
Our algorithm took 6 hours to finish with $4000$ control points for the model and $600\times 600$ resolution for the caustic image. 
A picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.
\begin{figure}
	\centering
 	\includegraphics[width=0.3\textwidth]{figure/caustic.jpg}
\caption{Teapot with a caustic image.}
\label{fig:caustic}
\end{figure}

\subsection{Subsurface Scattering and Deformation}
We first replicated \cite{Bickel:2010} to 
print materials with specified elasticity.
We then combined it with subsurface scattering
matching to print material that approximates
both the subsurface scattering property and the deformation behavior.
The result is shown in Figure~\ref{fig:deform}.
%We tried different combinations of generators in this experiment.
%We compared the performance of these different generator
%in terms of run-time and error.
\begin{enumerate}
\item Spline for top layer, fine-grained voxelization for mid layer
and a coarse grid for bottom layer.
\item Voxels for top layer, splines for middle layer and a coarse
bottom layer.
\item Find-grained voxels for top layer and coarse grid for bottom layer.
\end{enumerate}

@@
